\chapter*{Summary}
\addcontentsline{toc}{chapter}{Summary}

\hspace{\parindent}  In recent years, the banking sector has seen a significant push towards digital transformation, requiring innovative solutions to meet evolving technological demands.

This report presents the development of Fawri-CMS, a cutting-edge digital solution tailored for the banking industry, developed within the company B3G as part of my final graduation internship. A CMS, or Content Management System, allows users to create, manage, and modify content on a website without needing extensive technical knowledge. Fawri-CMS simplifies application development through a Low-Code approach, which utilizes visual development tools and pre-configured templates, enabling developers to create robust applications with minimal hand-coding and seamlessly integrating complex business processes. The system offers advanced CMS features such as content creation, management, and publication, designed to meet stringent security and compliance requirements.

The project followed an agile project management methodology, specifically the SCRUM
framework, enabling iterative development and regular feedback. We began with a detailed analysis and design phase, utilizing UML diagrams to model the system’s architecture. This was followed by technical design and the setup of the development environment, including SQL Server and .NET Core.
The development process involved the implementation of Domain-Driven Design (DDD) principles to ensure the robustness and maintainability of the system. A significant part of the form-building functionality, which allows for drag-and-drop components, was developed using JavaScript. This component was then published to npm and subsequently imported into our .NET solution, integrating seamlessly with the broader CMS features.

\noindent\rule[2pt]{\textwidth}{0.5pt}

{\textbf{Keywords :}}
Banking sector, digital transformation, Low-Code approach, business
processes, CMS, SQL Server, .NET Core, DDD.
\\
\noindent\rule[2pt]{\textwidth}{0.5pt}